The problem and promise of scale in multilayer networks

### 2020-01-23 paper/manuscript.Rmd
add grainchanger ref
affiliations

---
title: The problem and promise of scale in multilayer networks
author: Alec L. Robitaille, Quinn M.R. Webber, Julie W. Turner, Eric Vander Wal
output: 
    #word_document
    github_document
---

@@

To assess the influence of spatial scale on multilayer networks, we re-sampled our landcover classification map at varying scales. Specifically, we selected scales relevant to caribou ecology. We re-sampled landcover using the `grainchanger` **package/function[???]** (REF) at **five** scales: 100m, 250m, 500m, 1000m, 2500m. Sampling at 100 and 250m represents fine-scale decision making for caribou during foraging (REF), while re-sampling at 1000m and 2500m represents the scale at which caribou tend to select and avoid habitat (Bastille-Rousseau et al. 2017). Resampling occurred based on a modal moving window method, where **XXXXX. [ALEC YOU'RE GOING TO HAVE TO ADD DETAIL HERE]**

>>>>

---
title: The problem and promise of scale in multilayer networks
author: Alec L. Robitaille^1^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
header-includes: ^1^Department of Biology, Memorial University of Newfoundland, Canada; ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland

output: 
    #word_document
    github_document
---

@@

To assess the influence of spatial scale on multilayer networks, we re-sampled our landcover classification map at varying scales. Specifically, we selected scales relevant to caribou ecology. We re-sampled landcover using the `grainchanger` **package** (Graham 2019) at **five** scales: 100m, 250m, 500m, 1000m, 2500m. Sampling at 100 and 250m represents fine-scale decision making for caribou during foraging (REF), while re-sampling at 1000m and 2500m represents the scale at which caribou tend to select and avoid habitat (Bastille-Rousseau et al. 2017). Resampling occurred based on a modal moving window method, where **XXXXX. [ALEC YOU'RE GOING TO HAVE TO ADD DETAIL HERE]**
